Who Needs Privacy?

### 2019-02-12 manuscript/manuscript.tex
- Major changes regarding everything: analyses (e.g., inclusion of bifactor models), ms, etc.

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Who Needs Privacy?},
            pdfauthor={Tobias Dienlin~\& Miriam Metzger},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Who Needs Privacy?}
    \author{Tobias Dienlin\textsuperscript{1}~\& Miriam Metzger\textsuperscript{1,2}}
    \date{}

\shorttitle{Who Needs Privacy?}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of California, Santa Barbara}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\authornote{Add complete departmental affiliations for each
author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to Tobias
Dienlin, University of Hohenheim, Department of Media Psychology (540F).
E-mail:
\href{mailto:tobias.dienlin@uni-hohenheim.de}{\nolinkurl{tobias.dienlin@uni-hohenheim.de}}}

\abstract{
Objective: This study analyzes how personality relates to peoples'
desire for privacy. Specifically, we investigated whether the syllogism
``I don't mind surveillance because I have nothing to hide'' is correct:
Do people who lack integrity (given they have something to hide) indeed
desire more privacy?

Method: Study 1 featured an online questionnaire (\emph{N} = 268,
\emph{M}\textsubscript{age} = 20 years, 72\% female) and Study 2 a
laboratory experiment (\emph{N} = 87, \emph{M}\textsubscript{age} = 20
years, 51\% female), where participants wrote an essay about past
negative, positive, or neutral behaviors to analyze effects on desire
for privacy.

Results: Study 1 showed that respondents who are more shy, less anxious,
and more risk averse desired more privacy. Respondents who self-reported
lacking integrity reported desiring more privacy from government and
more anonymity. Study 2 replicated these results and showed a
statistical trend (\emph{p} = .052) that writing about negative past
behaviors increased desire for interpersonal privacy. Moreover, the
integrity IAT showed significant relations with desire for privacy from
government.

Conclusion: It is possible to predict peoples' desire for privacy based
on their lack of integrity. However, other neutral personality facets
also explain desire for privacy. Hence, putting everyone who desires
privacy under general suspicion would be incorrect.

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

In his novel \emph{The Circle}, ({\textbf{???}}) describes a dystopian
society in which people are gradually forfeiting their privacy. People
decide to become \enquote{transparent}, which means that they start
carrying a small camera around the neck in order to broadcast their
daily lives to the Internet. Eventually, this causes a societal
upheaval: \enquote{The pressure on those who hadn't gone transparent
went from polite to oppressive. The question, from pundits and
constituents, was obvious and loud: If you aren't transparent, what are
you hiding?} ({\textbf{???}}). The main argument being offered to
justify the surveillance is: \enquote{If you have nothing to hide, you
have nothing to fear.} This syllogism is familiar, given that it
commonly appears in also nonfictional conversations ({\textbf{???}}).
Consider, for example, the following tweet: \enquote{I don't download
illegally. I don't have anything on my comp{[}uter{]} to hide. Hell, I'm
sure the \#NSA gave up on me years ago.} ({\textbf{???}}).

Why do people desire privacy? To date there is only little research on
why people desire privacy and how the desire for privacy can be
predicted by aspects of personality. For example, and to the best of our
knowledge, so far no study exists that has analyzed the nothing-to-hide
argument from a scientific and empirical perspective. Why do some people
not care whether government agencies such as the NSA are collecting
their data ({\textbf{???}}), and why do others protest vehemently in
order to protect their privacy?

Answering this question is important: Given that government agencies are
collecting large amounts of data hoping to reduce criminality and
terrorism, and given that government agencies are collecting this data
preemptively and without concrete suspicions, it is relevant to find out
whether this practice of mass surveillance can be justified based on the
nothing-to-hide argument. As a result, the main question of this paper
is: Do people who desire more privacy really have more to hide and, more
generally, what are personality facets that determine peoples' overall
desire for privacy?

\hypertarget{desire-for-privacy}{%
\subsection{Desire for Privacy}\label{desire-for-privacy}}

Privacy captures the extent of voluntary withdrawal from others (Westin,
1967). Several models suggest that privacy is a multi-dimensional
concept: For example, in a theory-driven treatise ({\textbf{???}})
argued that privacy has four dimensions: informational, social,
psychological, and physical privacy. Pedersen (1979), by contrast, did
an empirical factor analysis (initially starting with 94 items) and
suggested that privacy exists on six dimensions: reserve, isolation,
solitude, intimacy with friends, intimacy with family, and anonymity. In
addition, Schwartz (1968) differentiated between horizontal and vertical
privacy: Whereas horizontal privacy captures withdrawal from peers,
vertical privacy refers to withdrawal from superiors or institutions
(e.g., government agencies). Next to being multi-dimensional, privacy is
also contingent (Dienlin, 2014): One can, for example, distinguish
between the objective privacy context, the subsequent subjective
perception of privacy, the psychological desire for privacy (which is
both a situational and dispositional need), and the resulting privacy
behavior (as represented by self-disclosure). For the purpose of this
study, we combine the aforementioned theories and focus on (a) vertical
privacy with regard to the desire for withdrawal from government
surveillance, (b) horizontal privacy in terms of the desire for
withdrawal from peers, friends, or acquaintances, and (c) both
horizontal and vertical privacy as captured by the general desire for
anonymity.

\hypertarget{the-relation-between-integrity-and-desire-for-privacy}{%
\subsubsection{The relation between integrity and desire for
privacy}\label{the-relation-between-integrity-and-desire-for-privacy}}

Which specific aspects of personality help predict desire for privacy?
At its core, the nothing-to-hide argument implies that lack of integrity
is an important predictor of why people desire privacy. This becomes
especially apparent when we consider the definition of Solove's (2007)
nothing-to-hide argument (notably, Solove is a strong critic of the
nothing-to-hide argument):

The NSA surveillance, data mining, or other government information
gathering programs will result in the disclosure of particular pieces of
information to a few government officials, or perhaps only to government
computers. This very limited disclosure of the particular information
involved is not likely to be threatening to the privacy of law-abiding
citizens. Only those who are engaged in illegal activities have a reason
to hide this information. {[}({\textbf{???}}); p.~753{]}

This definition helps illustrate the link between lack of integrity and
desire for privacy: People who have \enquote{engaged in illegal
activities} can be considered, by definition, to lack integrity
({\textbf{???}}), which is why they have a reason \enquote{to hide this
information} (or, in other words, to desire more privacy). In terms of a
scientific definition of integrity there is no real consensus, however
most scholars agree that integrity \enquote{incorporates a tendency to
comply with social norms, avoid deviant behavior, and embrace a sense of
justice, truthfulness, and fairness} {[}({\textbf{???}}); p.~82{]}.

Several theoretical arguments exist why lack of integrity might
correlate with desire for privacy. In general, any self-disclosure is a
potential risk because others might disagree, disapprove, or misuse the
information in other contexts ({\textbf{???}}). Privacy regulation
theory showed that if self-disclosures are too risky, people raise their
desired level of privacy, intensify their boundary regulation, and
employ more mechanisms to seclude and protect themselves
({\textbf{???}}). In traditional contexts, this could range from
moderate behaviors like closing doors, to extreme behaviors such as
physically tossing someone out of the room ({\textbf{???}}). In modern
contexts, protecting one's privacy can mean to avoid photographs or to
deliberately shun public places that have surveillance cameras. People
who have actually committed something bad, treacherous, or illegal
become even more vulnerable and face a significant risk of
self-disclosure, because others will surely disapprove of these
activities ({\textbf{???}}). Hence, the foregoing arguments illuminate
an indirect link between integrity and desire for privacy: By
definition, people who participate in negative activities are considered
to lack integrity ({\textbf{???}}). People who have engaged in negative
activities have, by definition, more to hide, and disclosures concerning
those activities pose a high risk. Because of this increased risk,
people will arguably desire more privacy, as a means to mitigate their
felt risk ({\textbf{???}}). In this way, the current research extends
Altman's privacy regulation theory (1976) by suggesting that lack of
integrity is an important yet unexamined factor that could increase
peoples' desired level of privacy.

A few studies can be found that imply a relation between privacy and
integrity. For example, several studies found that surveillance reduces
cheating behaviors ({\textbf{???}}, Covey.1989). ({\textbf{???}}) asked
students to solve an impossible maze. In the high surveillance
condition, the experimenter stood in front of the students and closely
monitored their behavior. In the low surveillance condition, the
experimenter stood behind the students, did not monitor their behavior,
and visual dividers were used to block the experimenter's view of the
students. Results showed that students were more likely to cheat in the
low surveillance condition, suggesting that in situations of
surveillance (i.e., less privacy), people show fewer cheating behaviors
(i.e., more integrity). Similarly, people are more likely to prevent
others from stealing when security cameras are visible ({\textbf{???}}),
which is also a sign of higher integrity. Next, in a longitudinal sample
with 457 respondents in Germany ({\textbf{???}}), people who reported
needing more privacy were less satisfied with their lives (\emph{r} =
-.47), had more (\emph{r} = .41) and less positive affect (\emph{r} =
-.39). More importantly however, people who felt they needed more
privacy were also less authentic on their SNSs profiles (\emph{r} =
-.48) and less authentic in their personal relationships (\emph{r} =
-.28; {\textbf{???}}). For example, people who agreed to items like
\enquote{I do not talk about personal issues unless my conversation
partner brings them up first} were more likely to report that their
online profiles did not truly represent their personality. Given the
argument that authenticity is a subset of integrity ({\textbf{???}}), we
reason that the concept of integrity might relate to the desired level
of privacy. Finally, Pedersen (1982) showed that three dimensions of
need for privacy related to self-esteem: In his study with \emph{N} = 70
undergraduate students, respondents who held a lower self-esteem were
more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21)
and preferred solitude (\emph{r} = .24). Granted, self-esteem and
integrity are generally distinct concepts; however, Pedersen's specific
operationalization of self-esteem integrated several aspects of
integrity (e.g., by using items such as \enquote{moral, nice, fair,
unselfish, good, honest, reputable, sane} to measure self-esteem). Thus,
our overarching hypothesis is that people who lack integrity have a
greater desire for privacy.

In Study 1, we used a questionnaire-based design to analyze how lack of
integrity and other personality facets relate to desire for privacy. In
accordance with the reasoning mentioned above, we suggest that people
with less integrity feel a greater desire for privacy. Specifically, we
argue that integrity may relate to the desire for privacy from (a)
government surveillance, as governments have the legitimate power to
prosecute illegal activities. Next, we hypothesize that integrity
relates to the desire privacy for (b) anonymity. Anonymity makes it more
difficult for both legal and social agents to identify and address
potential wrongdoers, which is why people with less integrity will
prefer situations in which they are anonymous. Finally, lack of
integrity likely also relates to an increased desire for privacy from
(c) other people, as most other people will disapprove of immoral or
illegal activities, and might reveal those activities to authorities.

Hypothesis 1: People who feel lower in self-perceived integrity desire
more privacy from government surveillance (H1a), more anonymity (H1b),
and more privacy from other persons (H1c).

\hypertarget{shyness}{%
\subsubsection{Shyness}\label{shyness}}

Critics of the nothing-to-hide argument hold that people who desire
privacy should not automatically be confronted with suspicion, and that
privacy has several purposes that are not related to criminal behavior
({\textbf{???}}). Westin (1967), for example, defined four primary
purposes of privacy: (1) self-development (i.e., the integration of
experiences into meaningful patterns), (2) autonomy (i.e., the desire to
avoid being manipulated and dominated), (3) emotional release (i.e., the
release of tension from social role demands), and (4) protected
communication (i.e., the ability to foster intimate relationships).
These are all important social factors for which people desire privacy.
Hence, the argument is that people who desire privacy can have several
legitimate reasons for doing so; reasons which are essential for
psychosocial wellbeing and which relate to different factors of
personality. Below, we thus explore other (neutral) aspects of
personality that potentially predict desire for privacy. In order to be
more precise, we follow the advice by Paunonen and Ashton (2001) and,
instead of using generic personality factors as predictors, refer to
specific personality facets.

First, we argue that people who are more reserved, who feel less
comfortable in social situations, generally desire more anonymity and
more interpersonal privacy. Given that privacy is, by definition, a
voluntary withdrawal from society (Westin, 1967), we expect that people
who are more reserved or more shy desire more privacy from others.
Several empirical studies support this hypothesis: Extroverted people
desire less privacy ({\textbf{???}}), people who describe themselves as
introverted thinkers are more likely to prefer social isolation
(Pedersen, 1982), and introverted people are more likely to report
invasions of privacy ({\textbf{???}}). Finally, we did not find
convincing theoretical and empirical arguments for why shyness should
relate to an increased desire for privacy from government surveillance,
which is why we did not include a hypothesis on this relation.

Hypothesis 2: People who are more shy desire more anonymity (H2a) and
more privacy from other persons (H2b).

@@

Of course, there are also reasons why people might desire less privacy.
Government agencies often curtail privacy with the aim to prevent crime:
For example, the NSA's surveillance programs are often considered a
direct response to the 9 / 11 terrorists attacks ({\textbf{???}}). It
seems plausible that people who are more afraid of terrorist attacks are
also more likely to consent to these surveillance programs, given that
these programs promise to reduce the likelihood of future attacks. One
can then argue that people who are afraid of terrorist attacks are also
more afraid of threats overall, which is why we suggest that people who
are, in general, more anxious desire less privacy from government
surveillance and less anonymity. We did not include a hypothesis on the
potential relation between anxiety and desire for interpersonal privacy.
On the one hand, one could argue that people who are more anxious are
more reserved, given that social interactions can pose significant risks
(especially with strangers or weak ties; {\textbf{???}}). At the same
time, one could suggest that especially those people who are more
anxious desire less privacy from others (and especially their strong
ties), in order to cope better with their daily challenges. At the end,
given that we measure interpersonal privacy on a general level (and do
not distinguish between desire for privacy from (a) weak ties and (b)
strong ties), it seems plausible that both effects could cancel each
other out.

Hypothesis 3: People who are more anxious desire less privacy from
government surveillance (H3a) and more anonymity (H3b).

@@

Disclosing personal information always poses a certain risk, given that
others can misuse self-disclosed personal information in different
contexts, which can lead to severe consequences ({\textbf{???}}). Not
everyone will feel intimidated by this hypothetical threat---except
those who have a general tendency to avoid taking unnecessary risks. The
most cautious strategy to minimize risks of personal self-disclosures
would be, arguably, to keep as much information as possible private.
Hence, we suggest that people who are, in general, more risk averse have
a good reason to desire more privacy in all three aforementioned
contexts.

Hypothesis 4: People who are more risk averse desire more privacy from
government surveillance (H4a), more anonymity (H4b), and more privacy
from other persons (H4c).

@@

The personal computer and the Internet have rendered the world
increasingly digitized: Social interactions, purchases, and medical
treatments nowadays all produce digital traces, which can be combined
into accurate latent user profiles. Given the features of digital
information (i.e., information is persistent, searchable, reproducible,
and scalable; {\textbf{???}}), this allows for unprecedented ways and
degrees of surveillance. Mark Zuckerberg famously observed that privacy
is no longer a \enquote{social norm,} rather that people share personal
information ({\textbf{???}}). Hence, in order to be part of contemporary
life (e.g., by using SNSs), it seems necessary to give up some privacy.
However, arguably not everyone is willing to pay that price, and
especially people who are more conservative might prefer to stick to
their usual routines and decide against giving up their privacy. This is
supported by empirical research: Older people, who are generally less
open and more traditional ({\textbf{???}}), are more concerned about
their privacy than younger people ({\textbf{???}}). Taken together, we
suggest that people who are more traditional also desire more privacy in
all three aforementioned contexts.

Hypothesis 5: People who are more traditional desire more privacy from
government surveillance (H5a), more anonymity (H5b), and more privacy
from other persons (H5c).

>>>>

\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Who Needs Privacy?},
            pdfauthor={Tobias Dienlin~\& Miriam Metzger},
            pdfkeywords={Privacy, need for privacy, personality, anonymity, integrity, SEM},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Who Needs Privacy?}
    \author{Tobias Dienlin\textsuperscript{1}~\& Miriam Metzger\textsuperscript{2}}
    \date{}

\shorttitle{Who Needs Privacy?}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of California, Santa Barbara}
\keywords{Privacy, need for privacy, personality, anonymity, integrity, SEM}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\authornote{Tobias Dienlin, Department of Media Psychology, University of Hohenheim, Germany; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.

Correspondence concerning this article should be addressed to Tobias Dienlin, University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany. E-mail: \href{mailto:tobias.dienlin@uni-hohenheim.de}{\nolinkurl{tobias.dienlin@uni-hohenheim.de}}}

\abstract{
This study analyzes how personality traits relate to need for privacy. We focus on three dimensions: (a) need for privacy from government surveillance, (b) need for privacy from other individuals, and (c) need for anonymity. Using an online questionnaire with 271 student respondents, several significant relationships were found. For example, results showed that less sociable people desired considerably more privacy on all three dimensions. Somewhat more controversially, people who reported less integrity also desired noticeably more anonymity. While anxious people desired slightly less privacy from government surveillance, risk avoidant people desired considerably more privacy from other people. Traditionalism did not relate to need for privacy. Together, the results have several implications. For example, they shed some light on the nothing-to-hide argument: A person who desires more anonymity might indeed be of less integrity. However, it is equally plausible that this person is just a little less sociable.

@@

\begin{document}
\maketitle

In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information (Sevignani, 2016), privacy has become a major topic of interest. Despite its importance, however, we still know surprisingly little about the relation between privacy and personality (e.g., Masur, 2018, p. 155). Why do some people need more privacy than others, and how do these people differ from one another? We think that a better understanding of the relation between personality and privacy is crucial: Several theories argue that personality determines privacy behaviors (e.g., Masur, 2018), however, to date there is almost no empirical research that can be used to deduct well-informed hypotheses. As a result, the main question of this paper is as follows: What are personality facets that can be used to best explain peoples' need for privacy?

\hypertarget{the-need-for-privacy}{%
\subsection{The Need for Privacy}\label{the-need-for-privacy}}

Privacy as a theoretical concept is both complicated and contested (Nissenbaum, 2010, p. 71). Hence, we begin by outlining our own understanding of privacy. First and foremost, privacy captures the extent of voluntary withdrawal from others (Westin, 1967). Several models suggest that privacy is multi-dimensional. For example, in a theory-driven treatise Burgoon (1982) argued that privacy has four dimensions: informational, social, psychological, and physical privacy. Pedersen (1979), by contrast, did an empirical factor analysis (initially starting with 94 items) and suggested that privacy exists on six dimensions: reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity. In addition, Schwartz (1968) differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies). Finally, one can also distinguish between the objective privacy context, the subjective privacy perception, the psychological need for privacy (which is both a situational and dispositional need), and the resulting privacy behavior (often represented by self-disclosure) (Dienlin, 2014).

For the purpose of this study, we combine the aforementioned notions and focus on (a) vertical privacy with regard to the need for withdrawal from government surveillance, (b) horizontal privacy in terms of the need for withdrawal from peers, friends, or acquaintances, and (c) both horizontal and vertical privacy as captured by the general need for anonymity.

In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually need privacy. Westin (1967) defined four primary positive purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships). Not least, privacy facilitates self-disclosure (Dienlin, 2014), which is vital for attaining social support, initiating relationships, and getting close to one another (Omarzu, 2000).

On the other hand, however, too much privacy can also be problematic. Because human beings are inherently social, being overly cut-off from others can impede flourishing, nurture deviant behavior, or introduce power asymmetries (Altman, 1975). \enquote{{[}T{]}he feminist critique rightfully argued that for men, the private sphere can be a shielded sphere in which female suppression is not sanctioned.} (DeCew, 1997, p. 81, as cited by Masur, 2018, p.~38). Next, and as mentioned above, privacy fosters self-disclosure. However, any self-disclosure is also always a potential risk because others might disagree, disapprove, or misuse the information in other contexts (Petronio, 2010).

\hypertarget{predicting-the-need-for-privacy}{%
\subsection{Predicting the Need for Privacy}\label{predicting-the-need-for-privacy}}

In what follows we now explore several personality aspects that we think might predict the need for privacy. As there is no established theory that dovetails privacy and personality, it is difficult to deduct precise and well-informed hypotheses. The rationales that we outline below should hence considered to be tentative suggestions. Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be found.

The general underlying theoretical framework that guided our selection process was the big five approach (e.g., John \& Srivastava, 1999). Note that privacy concerns, a variable conceptually close to need for privacy, shows only negligible relations with the big five factors (Bansal, Zahedi, \& Gefen, 2010; Junglas, Johnson, \& Spitzmüller, 2008). In order to be more precise, we hence follow the advice by Paunonen and Ashton (2001) and refer to specific personality facets instead of generic personality factors. To illustrate, instead of dwelling on the general factor of \emph{extraversion}, we instead focused on the facet \emph{gregariousness}, which we consider to be more pertinent.

Our reasoning was guided by another central theoretical thought. As implied above, privacy can be either positive or negative. Similarly, other people, the government, and anonymity can be considered either a \emph{resource} or a \emph{threat}. Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat. It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa (Altman, 1976).

\hypertarget{sociability}{%
\subsubsection{Sociability}\label{sociability}}

First, we argue that need for privacy should be closely related to a person's sociability or gregariousness (which is a subdimension of extraversion, John \& Srivastava, 1999). Sociability captures whether people prefer to spend their time alone or with company. It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity (e.g., Buss, 2001). Put differently, given that privacy is a voluntary withdrawal from society (Westin, 1967), we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.

This rationale is supported by several empirical studies: Extroverted people desire less privacy (Morton, 2013), people who describe themselves as introverted thinkers are more likely to prefer social isolation (Pedersen, 1982), and introverted people are more likely to report invasions of privacy (Stone, 1986).

More controversially, it has been argued that people need privacy because they have something to hide. The so-called nothing-to-hide argument states that \enquote{If you have nothing to hide, you have nothing to fear.} As described by Solove, the nothing-to-hide argument says that data mining and surveillance by government entities \enquote{is not likely to be threatening to the privacy of law-abiding citizens. Only those who are engaged in illegal activities have a reason to hide this information} (Solove, 2007, p. 753). Hence, another potential predictor of why people need privacy could also be a so-called \enquote{lack of integrity}.

Because integrity is a delicate concept, let us first try to define it conceptually. Although in terms of a scientific definition there is no consensus, most scholars seem to agree that integrity \enquote{incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness} (Connelly, Lilienfeld, \& Schmeelk, 2006, p. 82). In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow Paunonen (2002) and adopt a lowest common denominator approach, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.

It is indeed possible to think of theoretical arguments for why lack of integrity might correlate positively with need for privacy. People who have actually committed crimes evidently face even greater risk from self-disclosure compared to others, because government agencies and people sould surely disapprove of their activities (Petronio, 2010). Hence, the government and other people are more likely to be a threat, which should render anonymity rather a resource. As a consequence, people with lower integrity might desire more privacy as a means to mitigate their felt risk (Altman, 1976).

There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity. For example, studies have found that surveillance can reduce cheating behaviors (Corcoran \& Rotter, 1987; Covey, Saladin, \& Killen, 1989). Covey et al. (1989) for example asked students to solve an impossible maze. In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. In the low surveillance condition, the experimenter remained behind the students where he or she could not see the students. Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more integrity (i.e., fewer cheating behaviors). Next, in a longitudinal sample with 457 respondents in Germany (Trepte, Dienlin, \& Reinecke, 2013), people who felt they needed more privacy were also less authentic on their SNSs profiles (\emph{r} = -.48) and less authentic in their personal relationships (\emph{r} = -.28). Given the argument that authenticity is a subset of integrity (Sheldon, 2004), one could hence reason that also the concept of integrity might relate to a person's need for privacy. Somewhat related, it has been found that people who are more agreeable are also moderately less concerned about their privacy (Junglas et al., 2008). Finally, Pedersen (1982) showed that three dimensions of need for privacy relate to self-esteem: Respondents who held a lower self-esteem were more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21), and preferred solitude (\emph{r} = .24). While self-esteem and integrity are distinct concepts, Pedersen's specific operationalization of self-esteem integrated several aspects of integrity by using items such as \enquote{moral, nice, fair, unselfish, good, honest, reputable, sane}..

In conclusion, we could imagine that lack of integrity may indeed relate to an increased need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities. Next, it seems plausible that lack of integrity relates to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers. Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.

@@

Next, it seems possible that the need for privacy is also related to people's level of general anxiety (which is a subdimension of neuroticism, John \& Srivastava, 1999). General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened. With regard to interpersonal privacy, one could argue that people who are anxious are more likely to feel that social interactions pose a greater risk and threat (especially with strangers or weak ties; Granovetter, 1973), which is why anxious people might desire more privacy. Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are also more likely to withdraw online, for example by deleting posts or untagging themselves from linked content (Dienlin \& Metzger, 2016). On the other hand, one could argue in favor of the opposite: People who are more anxious may desire \emph{less} privacy from others (especially their strong ties), as a means to cope better with their daily challenges.

Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy. Despite the fact that only 18\% of all US-Americans trust their government \enquote{to do what is right} (Pew Research Center, 2017), almost everyone agrees that \enquote{it's the government's job to keep the country safe}, with most people also being satisfied with the government's job (Pew Research Center, 2015). Hence, when being anxious, the government should rather be seen as a resource than a threat. It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that these programs promise to prevent crime or to reduce the likelihood of terrorist attacks (Greenwald, 2013), implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.

@@

Similarly, it could be that need for privacy is related to the general tendency to avoid risks, to deliberate, and to plan carefully (deliberation is a subdimension of conscientiousness, John \& Srivastava, 1999). Risk avoidance captures the degree to which people prefer to abstain from taking risks. If other people are considered a threat, people who are risk averse should desire more interpersonal privacy, because they may feel greater risk associated with disclosure of personal information. The most cautious strategy to minimize risks of information disclosure would be, arguably, to keep as much information as possible private. Somewhat related, empirical studies report that people who think that their privacy is at risk are less likely to disclose information online (e.g., Bol et al., 2018). Moreover, research suggests that conscientious people are slightly more concerned about their privacy (Junglas et al., 2008). But again, especially with regard to privacy from government surveillance, risk averse people could also desire \emph{less} privacy, in order for the government to be able to avert potential threats.

@@

Next, it seems plausible that need for privacy is also related to traditionality (which is a subdimension of openness to experience, John \& Srivastava, 1999). Traditionalism measures whether people prefer to stick with their usual routines. The computers and the Internet have rendered the world increasingly knowable: Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles. Given that digital information is persistent, searchable, reproducible, and scalable (boyd, 2008), this allows for unprecedented means and degrees of surveillance. Mark Zuckerberg famously observed that privacy is no longer a social norm, rather the norm is that people share personal information (Johnson, 2010). Hence, in order to be part of contemporary life, it seems necessary to give up some privacy. However, people may not be equally willing to pay that price, and especially people who are more traditional might decide against giving up their privacy.

Empirical research does find that older people, who are generally less open and more traditional (Donnellan \& Lucas, 2008), are more concerned about their privacy (Fife \& Orjuel, 2012). On the other hand, Junglas et al. (2008) report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite. Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three aforementioned contexts.

\hypertarget{socio-demographic-variables}{%
\subsubsection{Socio-demographic variables}\label{socio-demographic-variables}}
